---
title: "Practical Guide for Using AgriPoliS"
author: "Mark Brady"
date: "`r Sys.Date()`"
output:  html_document           # rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
  )

library(tidyverse)
library(gridExtra) 
```

**NOTE: Can develop flowcharts with package diagrammeR**

# Procedures for creating a region: ~/region

The purpose of this paper is to document the steps for calibrating (creating) a new region in AgriPoliS,  including the sources of data. The main steps are:

- *upscaling*: representing the agricultural region
- *investments*: collate investment data
- *MIP_data*: collate market and technical data on production activities 
- *MIP_input*: develop static optimization model for each typical-farm type
- *dynamic_calibration*: validate the dynamic development of farmsin AgriPoliS


## Represent the structure of agriculture: ~/upscaling

Select typical farms and upscale to reprent the structure of agriculture in the region. 
Refer to Niklas cluster analysis.
Identifu farm structure data for the region

## Collate investment data: ~/investments


## Collate data on production activities: ~/MIP_data
Identify relevant production activities.
Main source of data AgriWise.

## Develop static optimization models: ~/MIP_input
Develop static optimization model for each typical-farm type

## Validate development of farms in AgriPoliS: ~/dynamic_calibration 
In this step we create the input files to run an AgriPoliS simulation and 
validate the reference scenario. The steps for creating these files are:

- *text*: creates input files.
- *policysettings*: create individual policy-settings files for simulating alternative policy scenarios.

### Creating input files: ~/text
The MS Excel workbook *Text_[region_name_short]_[YYYY-MM-DD].xlsm* is a macro-enabled workbook that contains a set of sheets for automaticall generating the input files in text format for simulating a region in AgriPoliS. The sheets are:

- *History*: document edits to workbook
- *globals*: global settings
- *options*: simulation options for specific regions, e.g., number of periods
- *translations*: for translating variable names that differ between inputfiles and AgriPoliS
- *farmsdata*: data characterizing the typical farms, e.g., areable area
- *market*: economic data for production activities, i.e., prices and variable costs
- *environmental*: data for biodiversity modelling
- *env_market*: data for calculating linear environmnetal indicators based on production activity levels.
- *yield*: coefficients of crop production functions for endogenous yields.
- *investments*: catalogue of investment activities and underlying data.
- *capacityLinks*: defines RHS of constraint rows in MIP matrix
- *matrix*: the generic MIP matrix for optimization of farm-agents decisions
- *matrixLinks*:values within the *matrix* can be influenced. Normally, used to calculate the share of bounded costs during a production period.
- *objFuncLinks*: All activities that are in the *matrix*, but not in the *market* or *investments* sheets must be listed here.
- *[farmID_0_first]...[farmID_last]*: initial investment capacities of the typical farms. One sheet per farm.

### farmsdata

```{r echo=FALSE}

```


```{r echo=FALSE}

input_dir <- "C:/AGRIPOLIS/regions/jonk/dynamic_calibration/text/inputfiles"

farmsdata <- read_tsv(paste0(input_dir,"/farmsdata.txt"))
farmsdata
```


# Procedures for simulating a region in AgriPoliS: ~/projects
To simulate a region in AgriPoliS requires an identical set of input files to those used in the dynamic calibration step. However, in adition to the reference policy scenario it is now necessary to define alternative policy scenarios.











## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
